Analytic Occultation Light Curves in Reflected Light

### 2020-04-13 tex/ms.tex
added W proof

\subsubsection{The vector $\viW$}
\label{sec:W}
%
The components of the vector $\viW$ are given by the integral
%
\begin{align}
    \label{eq:W}
    \iW_v(k^2, \vkappa) =
    \vint{\vkappa}{
        \cos\varphi\sin^{2v + 1}\varphi
        \left(1 - \frac{\sin^2\varphi}{k^2}\right)^\frac{3}{2}
    }
    \quad.
\end{align}
%
We may compute it by either upward or downward recursion. In the upward
case, we start with the lower boundary condition
%
\begin{proof}{}
    \iW_0 &= \Delta
    \Bigg\{
    \frac{\sinhalfkap[2]}{5}
    \left(
    \frac{1 - \mathbf{q}(k^2, \vkappa)^2}{1 - \mathbf{q}(k^2, \vkappa)^3}
    +
    \mathbf{q}(k^2, \vkappa)^3
    \right)
    \Bigg\}
    \quad.
\end{proof}
%
Defining
%
\begin{align}
    \mathbf{c}_0(k^2, \vkappa) & =
    \sinhalfkap[4]
    \frac{\mathbf{q}(k^2, \vkappa)^5}{1 - \mathbf{q}(k^2, \vkappa)^2}
    \quad,
\end{align}
%
we may recurse upward in $\iW$ and $\mathbf{c}$ simultaneously:
%
\begin{proof}{}
    \label{eq:Wv}
    \iW_v                      & =
    \frac{\Delta}{2v + 5}
    \left(
    \frac{2 v \sinhalfkap[2]}{1 - \mathbf{q}(k^2, \vkappa)^2}
    \iW_{v - 1}
    - \mathbf{c}_{v - 1}(k^2, \vkappa)
    \right)
    \nonumber
    \\
    \mathbf{c}_v(k^2, \vkappa) & =
    \sinhalfkap[2] \mathbf{c}_{v - 1}(k^2, \vkappa)
\end{proof}
%
for $v > 0$.
%
In the case of downward recursion, we start with the upper boundary
condition for $v = \vmax$,
%
\begin{proof}{}
    \label{eq:Wsol}
    \iW_\vmax &=
    \frac{\sin^{2\vmax + 2}\left(\frac{\vkappa}{2}\right)}{\vmax + \frac{5}{2}}
    \left(
    \mathbf{f}_\vmax(k^2, \vkappa)
    + 2 \mathbf{q}(k^2, \vkappa)^3
    \right)
    \quad,
\end{proof}
%
where
%
\begin{proof}{}
    \mathbf{f}_v(k^2, \vkappa)
    &\equiv
    \frac{3}{v+1}
    \,
    {_2\mathbf{F}_1}\left(
    -\frac{1}{2},
    v + 1;
    v + 2;
    1 - \mathbf{q}(k^2, \vkappa)^2
    \right)
\end{proof}
%
and ${_2\mathbf{F}_1}(a, b; c; \mathbf{z})$ is the Gauss
hypergeometric function.
We then recurse downward \xxx{...}
\xxx{TODO: Check these expressions.}

>>>>

\subsubsection{The vector $\viW$}
\label{sec:W}
%
The components of the vector $\viW$ are given by the integral
%
\begin{align}
    \label{eq:W}
    \iW_v(k^2, \vkappa) =
    \vint{\vkappa}{
        \cos\varphi\sin^{2v + 1}\varphi
        \left(1 - \frac{\sin^2\varphi}{k^2}\right)^\frac{3}{2}
    }
    \quad.
\end{align}
%
We may compute it by either upward or downward recursion. In both cases,
we compute each of the $\iW_v$ from
%
\begin{proof}{W}
    \iW_v(k^2, \vkappa) = \Delta \mathbf{b}_v(k^2, \vkappa)
    \quad.
\end{proof}
%
In the upward case, we start with the lower boundary conditions
%
\begin{proof}{W}
    \mathbf{b}_0(k^2, \vkappa) &=
    \frac{\sinhalfkap[2]}{5}
    \left(
    \frac{1 - \mathbf{q}(k^2, \vkappa)^3}{1 - \mathbf{q}(k^2, \vkappa)^2}
    +
    \mathbf{q}(k^2, \vkappa)^3
    \right)
    \nonumber \\
    \mathbf{c}_0(k^2, \vkappa) & =
    \sinhalfkap[4]
    \frac{\mathbf{q}(k^2, \vkappa)^5}{1 - \mathbf{q}(k^2, \vkappa)^2}
    \quad,
\end{proof}
%
and recurse upward in $\mathbf{b}$ and $\mathbf{c}$ simultaneously:
%
\begin{proof}{W}
    \mathbf{b}_v(k^2, \vkappa) & =
    \frac{1}{2v + 5}
    \left(
    \frac{2 v \sinhalfkap[2]}{1 - \mathbf{q}(k^2, \vkappa)^2}
    \mathbf{b}_{v - 1}(k^2, \vkappa)
    - \mathbf{c}_{v - 1}(k^2, \vkappa)
    \right)
    \nonumber
    \\
    \mathbf{c}_v(k^2, \vkappa) & =
    \sinhalfkap[2] \mathbf{c}_{v - 1}(k^2, \vkappa)
\end{proof}
%
for $v > 0$.
%
In the case of downward recursion, we start with the upper boundary
conditions
%
\begin{proof}{W}
    \mathbf{b}_\vmax &=
    \frac{\sin^{2\vmax + 2}\left(\frac{\vkappa}{2}\right)}{4\vmax + 10}
    \left(
    \mathbf{f}_\vmax(k^2, \vkappa)
    + 2 \mathbf{q}(k^2, \vkappa)^3
    \right)
    \nonumber \\
    \mathbf{c}_\vmax &=
    \frac{1}{2}
    \mathbf{q}(k^2, \vkappa)^5
    \sin^{2\vmax}\left(\frac{\vkappa}{2}\right)
    \quad,
\end{proof}
%
where
%
\begin{proof}{W}
    \mathbf{f}_v(k^2, \vkappa)
    &\equiv
    \frac{3}{v+1}
    \,
    {_2\mathbf{F}_1}\left(
    -\frac{1}{2},
    v + 1;
    v + 2;
    1 - \mathbf{q}(k^2, \vkappa)^2
    \right)
\end{proof}
%
and ${_2\mathbf{F}_1}(a, b; c; \mathbf{z})$ is the Gauss
hypergeometric function.
%
We recurse downward in $\mathbf{b}$ and $\mathbf{c}$ simultaneously:
%
\begin{proof}{W}
    \mathbf{b}_v(k^2, \vkappa) & =
    \frac{1 - \mathbf{q}(k^2, \vkappa)^2}{\sinhalfkap[2]}
    \left(1 + \frac{5}{2v + 2}\right)
    \mathbf{b}_{v + 1}(k^2, \vkappa) +
    \frac{\mathbf{c}_{v + 1}(k^2, \vkappa)}{v + 1}
    \nonumber
    \\
    \mathbf{c}_v(k^2, \vkappa) & =
    \frac{\mathbf{c}_{v + 1}(k^2, \vkappa)}{\sinhalfkap[2]}
    \quad.
\end{proof}
